---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AoC2017

<!-- badges: start -->
[![R-CMD-check](https://github.com/danhalligan/AoC2017/workflows/R-CMD-check/badge.svg)](https://github.com/danhalligan/AoC2017/actions)
<!-- badges: end -->

`AoC2017` is an R package that is intended to solve problems from
[Advent of Code 2017](https://adventofcode.com/2017). Some of the solutions
run relatively slowly and perhaps could be implemented better. In some cases,
I've used C++ to speed up the computations where I felt further optimisation
was not possible in R directly...

## Installation

You can install the released version of AoC2017 from
[GitHub](https://github.com/) with:

``` r
devtools::install_github("danhalligan/AoC2017")
```

## Example

To solve a specific day, you can use `solve_day`, passing in the input for
the current day.


``` r
library(AoC2017)
solve_day(day = 1, file = "day1-input.txt")
solve_day(file = "day1-input.txt")
```

If day is not provided it is guessed from the filename.

``` r
solve_day(file = "day1-input.txt")
```

Alternatively, some questions only require a short integer to be provided as
input:

```{r}
library(AoC2017)
solve_day(day = 3, input = 1024)
```
